% !TEX root = slides_ISSTA.tex
\section{Conclusion}
\subsection{recap}


\begin{frame}{Opportunities for future work!}

\onslide<2->
\begin{block}{Better Similarity Metrics}
Our similarity metric is empirical, can we do it analytically?
\end{block}


\onslide<3->

\begin{block}{Migration Support for Developers}
Supported regex features are different among languages.
\end{block}

\onslide<4->

\begin{block}{Identify Best Practices}
Could impact regex education and improve comprehension.
\end{block}


\onslide<5->
\begin{block}{Domain-Specific Support}
Does regex feature usage vary based on environment (IDE search, source code, text editor, database query, etc.)?
\end{block}

%\begin{block}{Refactoring Regular Expressions}
%Regexes are hard to read. Could refactoring help? 
%\end{block}


\end{frame}

\begin{frame}
\frametitle{Recap}

\begin{itemize}
\item Regexes are (sort of) everywhere! (42\% of Python projects)
\item (almost) Everyone writes regexes! (50\% of deves weekly)
\item Regexes are hard to read/write! (this is a pain point)
\end{itemize}

\onslide<2->
also...

\begin{itemize}
\item Current tools support most of the most common features
\item Regexes are often used for parsing/validating source code 
\item Many opportunities for future work!
\end{itemize}


\end{frame}


\begin{frame}
\Huge{\centerline{Questions?}}
\centering
\Large
Katie Stolee -- ktstolee@ncsu.edu

\vspace{24pt}
%\onslide<2->
(\textcolor{gray}{psst! Graduate students! I'm hiring!})
\end{frame}
\note[itemize]{
    \item pt 1
    \item pt 2
}

%----------------------------------------------------------------------------------------

\subsection{}
\begin{frame}
\frametitle{Survey vs. Repository}

How often do you use.... 

\begin{center}
\begin{tabular}{llcr}
\toprule
\textbf{Group} & \textbf{Code} &  \textbf{Survey} & \textbf{Repo Rank} \\  \hline 
endpoint anchors & (STR, END) & 4.4 & 7, 8\\ \hline 
capture groups & (CG) & 4.2 & 2 \\ \hline 
word boundaries & (WNW) & 3.5 & 22 \\ \hline 
lazy repetition & (LZY) &  2.9 & 15 \\ \hline 
(neg) look-ahead/behind &  (LKA, NLKA,  & 2.5 & 25, 21\\
& LKB, NLKB) & & 28, 27\\
\bottomrule
\end{tabular}

\textcolor{red}{Key: 6 = very frequently, 5 = frequently, 4 = occasionally, \\3 = rarely, 2 = very rarely, 1 = never}
\end{center}

\end{frame}


\end{document}
