\subsection{References}



\begin{frame}[allowframebreaks]
\frametitle{References}
\footnotesize{
\begin{thebibliography}{99}

\bibitem[Moller, 2010]{Brics} Moller, A. (2010).
\newblock dk.brics.automaton, finite\_state automata and regular expressions for Java.
\newblock http://www.brics.dk/automaton/.

\bibitem[Veanes, 2010]{Rex} Veanes, M., Halleux, P. d., and Tillmann, N. (2010).
\newblock Rex: Symbolic regular expression explorer.
\newblock In Proceedings of the 2010 Third International Conference on Software Testing, Verification and Validation, ICST ’10, pages 498\_507, Washington, DC, USA. IEEE Computer Society.

\bibitem[Kiezun, 2013]{Hampi} Kiezun, A., Ganesh, V., Artzi, S., Guo, P. J., Hooimeijer, P., and Ernst, M. D. (2013).
\newblock Hampi: A solver for word equations over strings, regular expressions, and context\_free grammars.
\newblock ACM Trans. Softw. Eng. Methodol., 21(4):25:1\_25:28.

\bibitem[Automata.Z3, 2016]{Automata.Z3} Loris Danto,Veanes, M., (2016).
\newblock Automata
\newblock https://github.com/AutomataDotNet/Automata

\bibitem[Van Dongen, 2012]{mcl} van Dongen, S. (2012)
\newblock MCL manual.
\newblock micans.org, 12\_068 edition.

\bibitem[bkiers, 2014]{pcre} bkiers (2014)
\newblock PCRE\_Parser
\newblock https://github.com/bkiers/pcre\_parser.

\bibitem[Python, 2016]{Python} Python (2016)
\newblock Python re module
\newblock https://docs.python.org/2/library/re.html.

\bibitem[regex101, 2016]{regex101} regex101 (2016)
\newblock regex101
\newblock https://regex101.com/.

\bibitem[Stolee, 2013]{comm} Stolee, K. T., Elbaum, S. (2013).
\newblock Identification, impact, and refactoring of smells in pipe\_like web mashups.
\newblock IEEE Trans. Softw. Eng., 39(12):1654\_1679.

%Images:

\bibitem[flickr, 2016]{knife} flickr (2016)
\newblock Swiss Army Knife Image
\newblock https://c2.staticflickr.com/4/3057/2383953694\_4b148d0a61.jpg.

\bibitem[pexels, 2016]{laptop} pexels (2016)
\newblock Laptop Image
\newblock https://static.pexels.com/photos/34600/pexels\_photo.jpg.

\bibitem[emerging, 2016]{emerging} emerging (2016)
\newblock Emerging Image
\newblock https://i.ytimg.com/vi/Gt\_5lS9hJFA/hqdefault.jpg.

\bibitem[BillOfSale, 2016]{BillOfSale} BillOfSale (2016)
\newblock BillOfSale Image
\newblock https://upload.wikimedia.org/wikipedia/commons/5/58/Bill\_of\_sale\_Louvre\_AO3765.jpg.

\bibitem[Doors, 2016]{Doors} Doors (2016)
\newblock Doors Image
\newblock http://ambcc.org/wp\_content/uploads/2014/11/OpenDoors.jpg.

\bibitem[TwoPaths, 2016]{TwoPaths} TwoPaths (2016)
\newblock TwoPaths Image (altered)
\newblock https://www.flickr.com/photos/james\_wheeler/9468151425.

\bibitem[galtonBoard, 2016]{gBoard} Galton\_Board (2016)
\newblock Galton\_Board
\newblock https://41.media.tumblr.com/deca33c79b8c4ae87b6d5cd1ffe25155/tumblr\_inline\_nmak5hmd9T1sh0dgh\_540.jpg.


\end{thebibliography}
}
\end{frame}
\note[itemize]{
    \item pt 1
    \item pt 2
}

%------------------------------------------------
