\subsection{Feature Analysis}

\begin{frame}
\frametitle{Basic Regex References Are Missing}
\begin{block}{feature usage statistics}
What features are more important when...
\\*\emph{building an analysis tool?}
\\*\emph{developing test regexes?}
\\*\emph{creating a toy language for a research project?}
\end{block}
\begin{block}{feature set summaries for variants and tools}
What features does each language and tool support...
\\*\emph{so I can port my regex code?}
\\*\emph{so I can choose the best fitting language?}
\\*\emph{so I can choose the best analysis tool?}
\end{block}
\end{frame}
\note[itemize]{
    \item pt 1
    \item pt 2
}

%------------------------------------------------

\begin{frame}
\frametitle{Why Python?}
\begin{enumerate}
\item back of envelope feature set comparision, seems like a good balance
\end{enumerate}
\end{frame}
\note[itemize]{
    \item pt 1
    \item pt 2
}

%------------------------------------------------

\begin{frame}
\frametitle{Project Selection}
\begin{enumerate}
\item picture of the 32 starting points
\item impl. issues limited size of dataset obtained
\end{enumerate}
\end{frame}
\note[itemize]{
    \item pt 1
    \item pt 2
}

%------------------------------------------------

\begin{frame}
\frametitle{Utilization Defined}
\begin{enumerate}
\item utl. image
\end{enumerate}
\end{frame}
\note[itemize]{
    \item pt 1
    \item pt 2
}

%------------------------------------------------


\begin{frame}
\frametitle{re module insights}
\begin{enumerate}
\item two tables
\end{enumerate}
\end{frame}
\note[itemize]{
    \item pt 1
    \item pt 2
}

%------------------------------------------------


\begin{frame}
\frametitle{PCRE Parsing Patterns}
\begin{enumerate}
\item that image
\end{enumerate}
\end{frame}
\note[itemize]{
    \item pt 1
    \item pt 2
}

%------------------------------------------------


\begin{frame}
\frametitle{Ranked features: Languages}
\begin{enumerate}
\item ranked features, eight languages combined, red circle around n guys, if possible
\end{enumerate}
\end{frame}
\note[itemize]{
    \item pt 1
    \item pt 2
}

%------------------------------------------------

\begin{frame}
\frametitle{Ranked features: Analysis Tools}
\begin{enumerate}
\item ranked features, four tools combined, red circle around n guys, if possible
\end{enumerate}
\end{frame}
\note[itemize]{
    \item pt 1
    \item pt 2
}

%------------------------------------------------


